Probability Distribution Checks

### 2017-07-23 Analysis.Rmd
Update Analysis to use percentage values, not severity scale
- Add disease progress curves in "graphs" directory

- Change the colours in the diagnostic plots to use ColorBrewer rather
than viridis for discrete colours, not continuous

```{r data_setup}
AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .cols = c("WMGT", "NRTE"))
```

@@

```{r 2015_TShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_15,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2015_LShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_severity_lmm_2015 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_15,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2016_TShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_16,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2016_LShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_severity_lmm_2016 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_16,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

>>>>

```{r data_setup}
AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .vars = c("WMGT", "NRTE"))
```

@@

```{r 2015_TShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_15,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2015_LShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_severity_lmm_2015 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_15,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2016_TShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_16,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

```{r 2016_LShB_severity}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_severity_lmm_2016 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_16,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

### 2017-07-23 Probability_distribution_checks.Rmd
Update Analysis to use percentage values, not severity scale
- Add disease progress curves in "graphs" directory

- Change the colours in the diagnostic plots to use ColorBrewer rather
than viridis for discrete colours, not continuous

```{r 2015_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$TShB_sev_AUDPS, "norm")
```

@@

```{r 2015_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_sev_AUDPS, "exp")
```

@@

```{r 2015_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$LShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$LShB_sev_AUDPS, "norm")
```

@@

```{r 2016_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$TShB_sev_AUDPS, "norm")
```

@@

```{r 2016_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$TShB_sev_AUDPS, "exp")
```

@@

```{r 2016_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$LShB_sev_AUDPS, "norm")
```

@@

```{r 2016_LShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$LShB_sev_AUDPS, "exp")
```

>>>>

```{r 2015_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$TShB_percent_AUDPS, "norm")
```

@@

2015 Tiller AUDPS is negative, so an exponential model will not fit

@@

```{r 2015_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$LShB_percent_AUDPS, "norm")
```

@@

```{r 2016_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$TShB_percent_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$TShB_percent_AUDPS, "norm")
```

@@

```{r 2016_TShB_percent_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_percent_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$TShB_percent_AUDPS, "exp")
```

@@

```{r 2016_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$LShB_percent_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$LShB_percent_AUDPS, "norm")
```

@@

```{r 2016_LShB_percent_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$LShB_percent_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$LShB_percent_AUDPS, "exp")
```
